Solar-Electric and Gas Powered, Long-Endurance UAV Sizing via Geometric Programming

### 2017-02-02 gassolarpaper/gassolarpaper.tex
fix no units text

For example, an aircraft optimized for $\pm$30 will have 11 different wind speed and solar flux constraints that must be satisfied, one for each degree of latitude between 20 and 30 degrees. 
Because wind speeds are low and solar flux is higher below 20 degrees latitude, no constraints for latitudes below 20 degrees are actually included in the optimization. 
Additionally, because long-endurance aircraft are likely to fly over land and the majority of land mass lies in the Northern Hemisphere, only wind speed data from the Northern Hemisphere is considered.
In total, 41 wind speed constraints were generated from 20-60 degrees North latitude. (See Appendix A) 
The constraint on wind speed and air density at the 35 degree latitude is

>>>>

For example, an aircraft optimized for $\pm$30 degrees latitude will have 11 different wind speed and solar flux constraints that must be satisfied, one for each degree of latitude between 20 and 30 degrees. 
Because wind speeds are low and solar flux is higher below 20 degrees latitude, no constraints for latitudes below 20 degrees are actually included in the optimization. 
Additionally, because long-endurance aircraft are likely to fly over land and the majority of land mass lies in the Northern Hemisphere, only wind speed data from the Northern Hemisphere is considered.
In total, 41 wind speed constraints were generated from 20-60 degrees North latitude. (See Appendix A) 
The constraint on wind speed and air density at the 35 degree latitude is
